Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-01-25 ms.tex
I put in a section describing the amplitude spectra I get if I put in a gith prior on the rotation period.

\clearpage
\pagebreak
\subsection{MCMC Time Series Fits}

Fitting all light curves to \sha\ with MCMC methods and without the A$_1$ > 0 prior results in more non-detections, but an unusual pattern to the spectra.
As with other MCMC fits, error bars are from photon and read noise, so they're likely under-estimated.

@@

@@

\appendix

>>>>

\clearpage
\pagebreak
\subsection{MCMC Time Series Fits - first try}

Fitting all light curves to \sha\ with MCMC methods and without the A$_1 >$ 0 prior results in more non-detections, but an unusual pattern to the spectra.
As with other MCMC fits, error bars are from photon and read noise, so they're likely under-estimated.

@@

\clearpage
\pagebreak
\subsection{MCMC Time Series Fits - second try}

As with my \texttt{IDL} code, I found that I had to impose a tight prior on the rotation period (I actually fixed it at the literature value of 4.1 hr) in order to avoid fitting the systematics at the telluric wavelengths.
When I do this, the MCMC code produces a very smooth amplitude spectrum for 2MASS 1821, as visible in Figure \ref{fig:ampSpecManualSTauRestrict}.
I experimented with the restriction that $3.8 < \tau < 4.0$ based on the multi-term Fourier series fits.
I used two different error scalings - 2.5 $\sigma$ and 4 $\sigma$.
2.5 $\sigma$ give the expected $\bar{\chi^2} \approx 1$, whereas 4 $\sigma$ gives around 0.4.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J1821 - 2.5$\times \sigma$]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0250perc_err_taurestrict.pdf}
	\label{fig:ampSpec0835times2p5ErrTauRest}
	}
\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0400perc_err_taurestrict.pdf}
	\label{fig:ampSpec1821fourTimesErr}
	}
	\caption{Restricting the $\tau$ parameter to, $3.8 < \tau < 4.0$ significantly reduces the long term quadratic terms' contribution to the sinusoidal fit. In this case, there were MCMC fits for \shb, one with error bars scaled by 2.5$\sigma$ and the other by 4.0$\sigma$.}
	\label{fig:ampSpecManualSTauRestrict}
	\vspace{0.1in}
\end{figure*}

@@

%\appendix
